Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-03-26 eg6-letters/long-paper/prc-dvcshelium.tex
Update figures

\begin{figure}[tbp]
\center
\includegraphics[width=15cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles \cite{Airapetian:2009cga} and theoretical predictions 
	from \cite{Liuti:2005gi} with full and dashed lines.}
\label{fig:CohALU90}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{fig3/Coherent_CFF.pdf}
	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
	$-t$ (right panels). The red full line red is the theoretical calculation from 
	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
	the blue dashed line is a calculation from Liuti {\it et 
	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
\label{fig:CohCFF}
\end{figure}

@@

The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
calculation presented also in Fig. \ref{fig:CohALU90}. The results are much more precise than 
the existing HERMES data and offer a strong constraint on the model presented. As in the
coherent case, the calculation appears to have issues to reproduce the shape of the data.
However, this time the calculation overshoots the data, sometimes by a significant amount.
An interesting way to look into this issue is to show the result on incoherent DVCS compared 
with the free proton. We can for instance make a ratio, in a fashion similar to the EMC 
effect, which allows to cancel out
the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
in Fig. \ref{fig:IncRatios}, where we observe again that most models significantly overshoot the data.

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.png}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.png}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.png}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares, HERMES 
	measurement \cite{Airapetian:2009cga} with green circles and the theoretical 
	calculation from \cite{Liuti:2005gi} with full lines.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.png}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.png}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.png}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares, HERMES 
	measurement \cite{Airapetian:2009cga} with green circles, the theoretical 
	calculation from \cite{Liuti:2005gi} with blue and red full lines and the
	calculation from \cite{Guzey:2008fe} with full and dashed black lines.}
\label{fig:IncRatios}
\end{figure}

@@

\begin{acknowledgments}
	%TODO Add Sergio and ERC!
 The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University.  M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
\end{acknowledgments}

>>>>

\begin{figure}[tbp]
\center
\includegraphics[width=17cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles \cite{Airapetian:2009cga}. Theoretical predictions 
	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, while the calculation from Fucini 
	{\it et al.}~\cite{Fucini:2018gso} is shown with a magenta long dash line.}
\label{fig:CohALU90}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{fig3/Coherent_CFF.pdf}
	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
	$-t$ (right panels). The red full line red is the theoretical calculation from 
	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
	the blue long dash line shows the predictions from Liuti {\it et 
	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
\label{fig:CohCFF}
\end{figure}

@@

The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
calculation presented also in Fig. \ref{fig:CohALU90}. We observe an important improvement
on the precisision compared to 
the HERMES data, which offers a strong constraint on the model presented. As in the
coherent case, the calculation appears to have issues to reproduce the shape of the data.
However, this time the calculation overshoots the data, sometimes by a significant amount.
An interesting way to look into this issue is to show the result on incoherent DVCS compared 
with the free proton. We can for instance make a ratio, in a fashion similar to the EMC 
effect, which allows to cancel out
the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
in Fig. \ref{fig:IncRatios}, where we observe again that most models significantly overshoot the data.

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, while the calculation from Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, the calculation from Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the
	the black dot-dash line is the calculation from Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}

@@

\begin{acknowledgments}
The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University. M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
\end{acknowledgments}
